Discovery of 47 $r$-process stars from the LAMOST survey

### 2018-02-02 article/ms.tex
newest draft for Andy

	At the two main absorption lines for Europium (4129\,\AA\ and 4205\,\AA) \todo{citation needed} we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors. Candidate Europium enhanced stars were selected by identifying stars that met the following criteria:

>>>>

	At two absorption lines for Europium (4129\,\AA\ and 4205\,\AA) we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors. Candidate Europium enhanced stars were selected by identifying stars that met the following criteria:
